---
title: "04 — Archetype Characterisation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(car)
library(fmsb)
```

## Load features, cluster assignments and outcome scores

```{r load-data}
# df <- read_csv("../../data/processed/lifestyle_features.csv")
# assignments <- read_csv("../../data/processed/cluster_assignments.csv")
# df <- df %>% left_join(assignments, by = "participant_id")
```

## Per-cluster summary statistics

```{r summary-stats}
# df %>% group_by(cluster) %>% summarise(across(<lifestyle_cols>, list(mean = mean, sd = sd), na.rm = TRUE))
```

## Statistical tests across clusters (ANOVA / chi-square)

```{r stat-tests}
# for (col in <numeric_cols>) {
#   model <- aov(df[[col]] ~ factor(df$cluster))
#   print(summary(model))
# }
```

## Relate clusters to PIU and mental health scores (train-set only, preliminary)

NOTE: use train-set labels only; report as a preliminary/exploratory association, not a
validated clinical finding.

## Robustness check: do associations hold under different clustering parameters?

Optional stretch: re-run notebooks 02/03 with different UMAP/clustering parameters and compare.

## Summary visualisation per archetype (radar chart / heatmap)

```{r radar-chart}
# One clear chart per archetype summarising its defining lifestyle features
# radarchart(archetype_summary_wide)
```

## Save archetype summary table

```{r save-summary}
# write_csv(archetype_summary, "../../data/processed/archetype_summary.csv")
```
